---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cookiemonster

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/cookiemonster)](https://CRAN.R-project.org/package=cookiemonster)
[![R-CMD-check](https://github.com/JBGruber/cookiemonster/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/JBGruber/cookiemonster/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/JBGruber/cookiemonster/branch/main/graph/badge.svg)](https://app.codecov.io/gh/JBGruber/cookiemonster?branch=main)
<!-- badges: end -->

Welcome to the `cookiemonster` package, your friendly solution to managing browser cookies in R! 🍪
Browser cookies are a way for browsers to recognise a user and their settings throughout sessions (e.g., if you accept a site's terms of service, this acceptance is saved as a cookie).
The focus of `cookiemonster` lies on making it possible to use these cookies from `R`to make request to the site (e.g., for web-scraping or automation).
If you are looking for a way to use cookies in shiny apps you can check out the [cookies package](https://CRAN.R-project.org/package=cookies).


## Installation

You can install the development version of `cookiemonster` from
[GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("JBGruber/cookiemonster")
```

```{r, child="vignettes/cookies.Rmd"}
```
